Measurement and Probability in Fuzzy Quantum Theories

### 2017-04-29 prop_iop.tex
prop_iop.tex \section{Expectation Values for IVPMs} Cleaning up proofs..

\subsection{Between Expectation Values for Classical and Quantum IVPMs}

@@

Notice that a sub-event space induced by any observable commutes so
that we can find a set~$\Omega$, a function~$\tau:\events'\rightarrow2^{\Omega}$
to pull quantum real-valued or interval-valued probability measures
to classical ones by theorem~\ref{thm:sub-event-space}. Although
it is a powerful tool, it would be more powerful if we can pull an
observable to a random variable as well.

@@

\begin{lemma}Adopting the definitions in this subsection. Given a
density matrix~$\rho$, there is a classical real-valued probability
measure~$\mu':2^{\Omega}\rightarrow\left[0,1\right]$ such that $\mu_{\rho}^{\mathrm{B}}=\mu'\circ\tau$.
Then, we have $\expval{\mathbf{O}}_{\rho}=\int X\rmd\mu'$.\end{lemma}

\begin{proof}
\begin{eqnarray*}
\expval{\mathbf{O}}_{\rho} & \stackrel{\textrm{Equation }(\ref{eq:quantum-expectation})}{=} & \sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}\lambda_{i}^{s}\mu_{\rho}^{\mathrm{B}}\left(P_{i}^{s}\right)\\
 & = & \sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}\lambda_{i}^{s}\mu'\left(\tau\left(P_{i}^{s}\right)\right)\\
 & \stackrel{\textrm{Equation }(\ref{eq:expectation})}{=} & \int X\rmd\left(\mu'\right)
\end{eqnarray*}
\end{proof}

\begin{lemma}Adopting the definitions in this subsection. Given a
quantum IVPM~$\bar{\mu}$, there is a classical real-valued probability
measure~$\bar{\mu}':2^{\Omega}\rightarrow\mathscr{I}$ such that
$\bar{\mu}=\bar{\mu}'\circ\tau$. Then, we have $\expval{\mathbf{O}}_{\bar{\mu}}=\int X\rmd\bar{\mu}'$.\end{lemma}

\begin{proof}
\begin{eqnarray*}
\expval{\mathbf{O}}_{\bar{\mu}} & \stackrel{\textrm{Equation }(\ref{eq:quantum-interval-expectation})}{=} & \sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}\lambda_{i}^{s}\left[\Delta\mul\left(P_{i}^{s\prime}\right),\Delta\mur\left(P_{i}^{s\prime}\right)\right]\\
 & = & \sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}\lambda_{i}^{s}\left[\Delta\mul[\prime]\left(\tau\left(P_{i}^{s\prime}\right)\right),\Delta\mur[\prime]\left(\tau\left(P_{i}^{s\prime}\right)\right)\right]\\
 & \stackrel{\textrm{Definition }\ref{def:Choquet}}{=} & \int X\rmd\bar{\mu}'
\end{eqnarray*}
\end{proof}

@@

\begin{proof}Since $\events'$ is induced by $\mathbf{O}$, it is
commuting. By theorem~\ref{thm:sub-event-space}, there is set~$\Omega$,
a function~$\tau:\events'\rightarrow2^{\Omega}$, and a convex classical
interval-valued probability measure~$\bar{\mu}':2^{\Omega}\rightarrow\mathscr{I}$
such that 
\begin{equation}
\bar{\mu}=\bar{\mu}'\circ\tau\textrm{ .}\label{eq:sub-event-space}
\end{equation}
Let $\mul[\prime]:\events'\rightarrow\left[0,1\right]$ and $\mur[\prime]:\events'\rightarrow\left[0,1\right]$
are the left-end and the right-end of $\bar{\mu}'$, respectively,
i.e., $\bar{\mu}'\left(E\right)=\left[\mul[\prime]\left(E\right),\mur[\prime]\left(E\right)\right]$
for all $E\in2^{\Omega}$. Consider the random variable~$X:\Omega\rightarrow\mathbb{R}$
defined by $X=\sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}\lambda_{i}^{s}\mathbf{1}_{\tau\left(P_{i}^{s}\right)}$.
Then, 
\begin{eqnarray*}
 &  & \expval{\mathbf{O}}_{\bar{\mu}}\\
 & \stackrel{\textrm{Equation }(\ref{eq:quantum-interval-expectation})}{=} & \sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}\lambda_{i}^{s}\left[\Delta\mul\left(P_{i}^{s\prime}\right),\Delta\mur\left(P_{i}^{s\prime}\right)\right]\\
 & \stackrel{\textrm{Equation }(\ref{eq:sub-event-space})}{=} & \sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}\lambda_{i}^{s}\left[\Delta\mul[\prime]\left(\tau\left(P_{i}^{s\prime}\right)\right),\Delta\mur[\prime]\left(\tau\left(P_{i}^{s\prime}\right)\right)\right]\\
 & \stackrel{\textrm{Definition }\ref{def:Choquet}}{=} & \int X\rmd\bar{\mu}'\\
 & \stackrel{\textrm{Theorem }\ref{thm:Rosenmuller}}{=} & \left[\min_{\mu'\in\mathrm{core}\left(\bar{\mu}'\right)}\int X\rmd\mu',\max_{\mu'\in\mathrm{core}\left(\bar{\mu}'\right)}\int X\rmd\mu'\right]\\
 & \stackrel{\textrm{Definition }\ref{def:Choquet}}{=} & \left[\min_{\mu'\in\mathrm{core}\left(\bar{\mu}'\right)}\sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}\lambda_{i}^{s}\mu'\left(\tau\left(P_{i}^{s}\right)\right),\max_{\mu'\in\mathrm{core}\left(\bar{\mu}'\right)}\sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}\lambda_{i}^{s}\mu'\left(\tau\left(P_{i}^{s}\right)\right)\right]\\
 & \stackrel{\textrm{Claim }\ref{claim:min-max-core}}{=} & \left[\min_{\mu\in\mathrm{core}\left(\bar{\mu},\events'\right)}\sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}\lambda_{i}^{s}\mu\left(P_{i}^{s}\right),\max_{\mu\in\mathrm{core}\left(\bar{\mu},\events'\right)}\sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}\lambda_{i}^{s}\mu\left(P_{i}^{s}\right)\right]\\
 & \stackrel{\textrm{Definition }\ref{def:consistent-state}}{=} & \left[\min_{\rho\in\coreBorn\left(\bar{\mu},\events'\right)}\sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}\lambda_{i}^{s}\mu_{\rho}^{\mathrm{B}}\left(P_{i}^{s}\right),\max_{\rho\in\coreBorn\left(\bar{\mu},\events'\right)}\sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}\lambda_{i}^{s}\mu_{\rho}^{\mathrm{B}}\left(P_{i}^{s}\right)\right]\\
 & \stackrel{\textrm{Equation }(\ref{eq:quantum-interval-expectation})}{=} & \left[\min_{\rho\in\coreBorn\left(\bar{\mu},\events'\right)}\expval{\mathbf{O}}_{\rho},\max_{\rho\in\coreBorn\left(\bar{\mu},\events'\right)}\expval{\mathbf{O}}_{\rho}\right]\textrm{ ,}
\end{eqnarray*}
where claim~\ref{claim:min-max-core} is going to be proved in the
next paragraph.

\begin{claim}\label{claim:min-max-core}
\begin{eqnarray}
\min_{\mu'\in\mathrm{core}\left(\bar{\mu}'\right)}\sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}\lambda_{i}^{s}\mu'\left(\tau\left(P_{i}^{s}\right)\right) & = & \min_{\mu\in\mathrm{core}\left(\bar{\mu},\events'\right)}\sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}\lambda_{i}^{s}\mu\left(P_{i}^{s}\right)\label{eq:min-core}\\
\max_{\mu'\in\mathrm{core}\left(\bar{\mu}'\right)}\sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}\lambda_{i}^{s}\mu'\left(\tau\left(P_{i}^{s}\right)\right) & = & \max_{\mu\in\mathrm{core}\left(\bar{\mu},\events'\right)}\sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}\lambda_{i}^{s}\mu\left(P_{i}^{s}\right)\label{eq:max-core}
\end{eqnarray}

\end{claim}

\begin{proof}Since equation~(\ref{eq:min-core}) and (\ref{eq:max-core})
are essentially the same, we are only going to prove equation~(\ref{eq:min-core}).

We have
\begin{equation}
\min_{\mu'\in\mathrm{core}\left(\bar{\mu}'\right)}\sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}\lambda_{i}^{s}\mu'\left(\tau\left(P_{i}^{s}\right)\right)\le\min_{\mu\in\mathrm{core}\left(\bar{\mu},\events'\right)}\sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}\lambda_{i}^{s}\mu\left(P_{i}^{s}\right)
\end{equation}
because the same $\tau$ in theorem~\ref{thm:sub-event-space} applies
to both real-valued and interval-valued probability measure, i.e.,
for any $\mu\in\mathrm{core}\left(\bar{\mu},\events'\right)$, there
exists a $\mu'\in\mathrm{core}\left(\bar{\mu}'\right)$ such that
$\mu=\mu'\circ\tau$.

On the other hand, 
\begin{equation}
\min_{\mu'\in\mathrm{core}\left(\bar{\mu}'\right)}\sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}\lambda_{i}^{s}\mu'\left(\tau\left(P_{i}^{s}\right)\right)\ge\min_{\mu\in\mathrm{core}\left(\bar{\mu},\events'\right)}\sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}\lambda_{i}^{s}\mu\left(P_{i}^{s}\right)
\end{equation}
because for any $\mu'\in\mathrm{core}\left(\bar{\mu}'\right)$, we
have 
\begin{eqnarray}
 &  & \mu'\left(E\right)\in\bar{\mu}'\left(E\right)\textrm{ for all }E\in2^{\Omega}\\
 & \Rightarrow & \mu'\left(\tau\left(P\right)\right)\in\bar{\mu}'\left(\tau\left(P\right)\right)=\bar{\mu}\left(P\right)\textrm{ for all }P\in\events'
\end{eqnarray}
Let $\rho=\sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}\frac{\mu'\left(\tau\left(P_{i}^{s}\right)\right)}{\Tr\left(P_{i}^{s}\right)}P_{i}^{s}$.
Then, we have 
\begin{eqnarray}
\mu_{\rho}^{\mathrm{B}}\left(P_{j}^{-}\right) & = & \sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}\frac{\mu'\left(\tau\left(P_{i}^{s}\right)\right)}{\Tr\left(P_{i}^{s}\right)}\Tr\left(P_{i}^{s}P_{j}^{-}\right)=\mu'\left(\tau\left(P_{j}^{-}\right)\right)\\
\mu_{\rho}^{\mathrm{B}}\left(P_{j}^{+}\right) & = & \sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}\frac{\mu'\left(\tau\left(P_{i}^{s}\right)\right)}{\Tr\left(P_{i}^{s}\right)}\Tr\left(P_{i}^{s}P_{j}^{+}\right)=\mu'\left(\tau\left(P_{j}^{+}\right)\right)
\end{eqnarray}
Therefore, $\mu_{\rho}^{\mathrm{B}}\in\mathrm{core}\left(\bar{\mu},\events'\right)$.\end{proof}\end{proof}

>>>>

\subsection{Between Expectation Values for Classical and Quantum IVPMs\label{subsec:Between-Expectation-Values-Classical-Quantum}}

@@

Notice that a sub-event space induced by any observable commutes.
By theorem~\ref{thm:sub-event-space}, we can find a set~$\Omega$,
a function~$\tau:\events'\rightarrow2^{\Omega}$ to pull quantum
real-valued or interval-valued probability measures to classical ones.
Although it is a powerful tool, it would be more powerful if we can
pull an observable to a random variable as well.

@@

\begin{lemma}\label{lemma:real-expectation-value-between-classical-quantum}Adopting
the definitions in this subsection. Given a density matrix~$\rho$,
there is a classical real-valued probability measure~$\mu':2^{\Omega}\rightarrow\left[0,1\right]$
such that $\mu_{\rho}^{\mathrm{B}}=\mu'\circ\tau$. Then, we have
$\expval{\mathbf{O}}_{\rho}=\int X\rmd\mu'$.\end{lemma}

\begin{proof}
\begin{eqnarray*}
\expval{\mathbf{O}}_{\rho} & \stackrel{\textrm{Equation }(\ref{eq:quantum-expectation})}{=} & \sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}\lambda_{i}^{s}\mu_{\rho}^{\mathrm{B}}\left(P_{i}^{s}\right)\\
 & = & \sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}\lambda_{i}^{s}\mu'\left(\tau\left(P_{i}^{s}\right)\right)\\
 & \stackrel{\textrm{Equation }(\ref{eq:expectation})}{=} & \int X\rmd\mu'\textrm{ .}
\end{eqnarray*}
\end{proof}

\begin{lemma}\label{lemma:interval-expectation-value-between-classical-quantum}Adopting
the definitions in this subsection. Given a quantum IVPM~$\bar{\mu}$,
there is a classical real-valued probability measure~$\bar{\mu}':2^{\Omega}\rightarrow\mathscr{I}$
such that $\bar{\mu}=\bar{\mu}'\circ\tau$. Then, we have $\expval{\mathbf{O}}_{\bar{\mu}}=\int X\rmd\bar{\mu}'$.\end{lemma}

\begin{proof}Let $\mul[\prime]:\events'\rightarrow\left[0,1\right]$
and $\mur[\prime]:\events'\rightarrow\left[0,1\right]$ are the left-end
and the right-end of $\bar{\mu}'$, respectively, i.e., $\bar{\mu}'\left(E\right)=\left[\mul[\prime]\left(E\right),\mur[\prime]\left(E\right)\right]$
for all $E\in2^{\Omega}$. Then, 
\begin{eqnarray*}
\expval{\mathbf{O}}_{\bar{\mu}} & \stackrel{\textrm{Equation }(\ref{eq:quantum-interval-expectation})}{=} & \sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}\lambda_{i}^{s}\left[\Delta\mul\left(P_{i}^{s\prime}\right),\Delta\mur\left(P_{i}^{s\prime}\right)\right]\\
 & = & \sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}\lambda_{i}^{s}\left[\Delta\mul[\prime]\left(\tau\left(P_{i}^{s\prime}\right)\right),\Delta\mur[\prime]\left(\tau\left(P_{i}^{s\prime}\right)\right)\right]\\
 & \stackrel{\textrm{Definition }\ref{def:Choquet}}{=} & \int X\rmd\bar{\mu}'\textrm{ .}
\end{eqnarray*}
\end{proof}

@@

\begin{proof}Adopting the definitions in subsection~\ref{subsec:Between-Expectation-Values-Classical-Quantum},
it is easy to prove
\begin{eqnarray*}
\expval{\mathbf{O}}_{\bar{\mu}} & \stackrel{\textrm{Lemma }\ref{lemma:real-expectation-value-between-classical-quantum}}{=} & \int X\rmd\bar{\mu}'\\
 & \stackrel{\textrm{Theorem }\ref{thm:Rosenmuller}}{=} & \left[\min_{\mu'\in\mathrm{core}\left(\bar{\mu}'\right)}\int X\rmd\mu',\max_{\mu'\in\mathrm{core}\left(\bar{\mu}'\right)}\int X\rmd\mu'\right]\\
 & \stackrel{\textrm{Lemma }\ref{lemma:interval-expectation-value-between-classical-quantum}}{=} & \left[\min_{\mu'\in\mathrm{core}\left(\bar{\mu}'\right)}\expval{\mathbf{O}}_{\rho},\min_{\mu'\in\mathrm{core}\left(\bar{\mu}'\right)}\expval{\mathbf{O}}_{\rho}\right]\textrm{ .}
\end{eqnarray*}
Therefore, equation~(\ref{eq:quantum-interval-expectation-core})
is equivalent to convexity if $\mathrm{core}\left(\bar{\mu}'\right)$
and $\coreBorn\left(\bar{\mu},\events'\right)$ are one-to-one correspondence
so that
\begin{equation}
\left[\min_{\mu'\in\mathrm{core}\left(\bar{\mu}'\right)}\expval{\mathbf{O}}_{\rho},\min_{\mu'\in\mathrm{core}\left(\bar{\mu}'\right)}\expval{\mathbf{O}}_{\rho}\right]=\left[\min_{\rho\in\coreBorn\left(\bar{\mu},\events'\right)}\expval{\mathbf{O}}_{\rho},\max_{\rho\in\coreBorn\left(\bar{\mu},\events'\right)}\expval{\mathbf{O}}_{\rho}\right]\textrm{ .}
\end{equation}

Notice that lemma~\ref{lemma:real-expectation-value-between-classical-quantum}
guarantees that for any $\rho\in\coreBorn\left(\bar{\mu},\events'\right)$,
there exists $\mu'\in\mathrm{core}\left(\bar{\mu}'\right)$ such that
$\mu_{\rho}^{\mathrm{B}}=\mu'\circ\tau$. On the other hand, for any
$\mu'\in\mathrm{core}\left(\bar{\mu}'\right)$, we have
\begin{eqnarray}
 &  & \mu'\left(E\right)\in\bar{\mu}'\left(E\right)\textrm{ for all }E\in2^{\Omega}\\
 & \Rightarrow & \mu'\left(\tau\left(P\right)\right)\in\bar{\mu}'\left(\tau\left(P\right)\right)=\bar{\mu}\left(P\right)\textrm{ for all }P\in\events'
\end{eqnarray}
Let $\rho=\sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}\frac{\mu'\left(\tau\left(P_{i}^{s}\right)\right)}{\Tr\left(P_{i}^{s}\right)}P_{i}^{s}$.
Then, we have 
\begin{eqnarray}
\mu_{\rho}^{\mathrm{B}}\left(P_{j}^{-}\right) & = & \sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}\frac{\mu'\left(\tau\left(P_{i}^{s}\right)\right)}{\Tr\left(P_{i}^{s}\right)}\Tr\left(P_{i}^{s}P_{j}^{-}\right)=\mu'\left(\tau\left(P_{j}^{-}\right)\right)\\
\mu_{\rho}^{\mathrm{B}}\left(P_{j}^{+}\right) & = & \sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}\frac{\mu'\left(\tau\left(P_{i}^{s}\right)\right)}{\Tr\left(P_{i}^{s}\right)}\Tr\left(P_{i}^{s}P_{j}^{+}\right)=\mu'\left(\tau\left(P_{j}^{+}\right)\right)
\end{eqnarray}
Therefore, $\mu_{\rho}^{\mathrm{B}}\in\mathrm{core}\left(\bar{\mu},\events'\right)$,
i.e., $\rho\in\coreBorn\left(\bar{\mu},\events'\right)$.\end{proof}
